### 2015-07-11 narrative/qos.tex
minor edits.

\subsubsection{Quality of Service (QoS)}
Our ultimate goal, rather than just performance predictability, is to offer
predictable Quality of Service (QoS) for the storage system.
%Performance quality can be expressed in either relative or absolute
%terms. Examples of relative performance terms are ``fair'',
%``proportional'', or ``priority/class-based'' (``the higher the
%priority the better the service'' or ``1st class is better than
%2nd''). The key advantage of relative performance terms is that
%they are easy to implement. The key disadvantage is the difficulty
%of making any guarantees based on those implementations --
%even relative guarantees are mired by the well-known effect of
%priority inversion~\cite{lampson:cacm80}. Examples of absolute
%performance terms are ``rate-based'', ``soft real-time'', and
%``hard real-time''. The key advantage of absolute performance
%terms are that they enable the implementation of strong
%guarantees: absolute terms enable agreements between application
%tasks and storage that we call \emph{reservations} and that do not
%change meaning depending
%on the storage system's workload. The key challenge of absolute
%performance terms is that their implementation is non-trivial,
%especially in large-scale systems.
One of the key differentiating features this project offers is driving storage
decisions through QoS~\emph{reservations} rather than continuing the current
model of allowing applications to compete freely without restriction for part
or all of the storage resources. The current approach leads to interference
effects~\cite{lofstead:2010:io-variability,liu_hotstorage} that can greatly
impact I/O performance predictability. 
%Further, with the introduction of additional tiers in the
%storage stack, the performance variability will increase with greater
%competiion for limited high performance resources. 
%% Temporaily commented out the above sentence, because it may not be true for
%the next DOE systems. 
Unfettered, this competition can yield lower system and application performance
than if applications attempt to reserve storage resources thereby enabling the
storage system to reason over its performance in terms of reservations and
actual performance.  In the cases where an application arrives that needs to
run more urgently than any of the other already running applications, the
system can rapidly respond to it by reducing the amount of resources taken by
less urgent applications, allowing the urgent application to finish, and later
reverting back to the previous committed resource level for the rest.  This can
be automatically enforced via user- or administrator- specified
\textit{policies}\S\ref{sec:data-description}.

>>>>

\subsubsection{Quality of Service (QoS)}
Our ultimate goal, rather than just performance predictability, is to offer
predictable QoS for the storage system.
%Performance quality can be expressed in either relative or absolute
%terms. Examples of relative performance terms are ``fair'',
%``proportional'', or ``priority/class-based'' (``the higher the
%priority the better the service'' or ``1st class is better than
%2nd''). The key advantage of relative performance terms is that
%they are easy to implement. The key disadvantage is the difficulty
%of making any guarantees based on those implementations --
%even relative guarantees are mired by the well-known effect of
%priority inversion~\cite{lampson:cacm80}. Examples of absolute
%performance terms are ``rate-based'', ``soft real-time'', and
%``hard real-time''. The key advantage of absolute performance
%terms are that they enable the implementation of strong
%guarantees: absolute terms enable agreements between application
%tasks and storage that we call \emph{reservations} and that do not
%change meaning depending
%on the storage system's workload. The key challenge of absolute
%performance terms is that their implementation is non-trivial,
%especially in large-scale systems.
One of the key differentiating features this project offers is driving storage
decisions through QoS~\emph{reservations} rather than continuing the current
model of allowing applications to compete freely without restriction for part
or all of the storage resources. The current approach leads to interference
effects~\cite{lofstead:2010:io-variability,liu_hotstorage} that can greatly
impact I/O performance predictability. 
%Further, with the introduction of additional tiers in the
%storage stack, the performance variability will increase with greater
%competiion for limited high performance resources. 
%% Temporaily commented out the above sentence, because it may not be true for
%the next DOE systems. 
Unfettered, this competition can yield lower system and application performance
than if applications attempt to reserve storage resources thereby enabling the
storage system to reason over its performance in terms of reservations and
actual performance.  In the cases where an application arrives that needs to
run more urgently than any of the other already running applications, the
system can rapidly respond to it by reducing the amount of resources taken by
less urgent applications, allowing the urgent application to finish, and later
reverting back to the previous committed resource level for the rest.  This can
be automatically enforced via user- or administrator- specified
\textit{policies}\S\ref{sec:data-description}.
